%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}

\begin{document} 
% ----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

    \begin{minipage}[t]{0.5\textwidth}
        \vspace{-\baselineskip} % Required for vertically aligning minipages

        { \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{John Stamp}}}} % First name

        \vspace{6pt}

        {\Large Engineering Manager $\sim$ Tech Lead} % Career or current job title
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
        \vspace{-\baselineskip} % Required for vertically aligning minipages

        % The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
        % \icon{Globe}{11}{\href{http://www.google.com}{portafolio.com}}\\
        \icon{Phone}{11}{+353 87 6551983}\\
        \icon{MapMarker}{11}{Dublin, Ireland}\\

    \end{minipage}
    \begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
        \vspace{-\baselineskip} % Required for vertically aligning minipages

        \icon{Envelope}{11}{\href{mailto:john.stamp@gmail.com}{john.stamp@gmail.com}}\\
        \icon{Github}{11}{\href{https://github.com/uma-dev}{github.com/johnstamp}}\\
        \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com}{/in/johnstamp}}\\

    \end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

    \begin{minipage}[t]{0.46\textwidth}
        \cvsect{Summary}
        \vspace{-6pt}
        \begin{flushleft}
            \textbf{Experienced Technical Lead} with a proven track record in designing and delivering scalable, 
            cloud-based systems across telecommunications, travel, and education sectors. 
            Skilled at leading cross-functional teams, modernizing legacy platforms, and executing high-impact projects with a balance of technical excellence and strategic insight. 
            Recognized for mentoring engineers, establishing best practices, and driving measurable improvements in performance, scalability, and overall quality.
        \end{flushleft}
    \end{minipage}
    \hfill % Whitespace between
    \begin{minipage}[t]{0.465\textwidth}
        \cvsect{Skills}
        \vspace{-6pt}

        \begin{minipage}[t]{0.2\textwidth}
            \textbf{Languages:}
        \end{minipage}
        \hfill
        \begin{minipage}[t]{0.73\textwidth}
            Java, Spring, Golang, Scala, Typescript, React, Rust.
        \end{minipage}
        \vspace{4mm}

        \begin{minipage}[t]{0.2\textwidth}
            \textbf{Technologies:}
        \end{minipage}
        \hfill
        \begin{minipage}[t]{0.73\textwidth}
            GCP, Docker, Kubernetes, Postgres, Microservices, GraphQL.
        \end{minipage}

    \end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
    \cvsect{Experience}
    \begin{entrylist}
        \entry
        {10/2021 -- 12/2024}
        {
            Tech Team Lead/ Engineering Manager
        }
        {Deem Ltd}
        {\vspace{-10pt}
        \begin{flushleft}
            Led the migration of legacy systems to a scalable, cloud-based architecture, significantly improving system performance and
            maintainability. Was technical lead for the GraphQL and React codebases. Promoted from Tech Lead to Engineering Manager in May 2024

        \end{flushleft}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=15pt]
                \item Stabilized and launched a React/GraphQL frontend application, ensuring seamless
                deployment with zero rollbacks over 12 months
                \item Architected and delivered an integration with Uber’s APIs, enabling
                seamless ride bookings within the deem app. I drove cross-team collaboration across three timezones, US, Dublin and Thailand. 
                Feature built using golang, microservices React and postgres.
                \item Increased React code coverage from 25 to 55, fostering a quality-first mindset within
                the team
                \item Designed and implemented robust Golang/Postgres microservices, enhancing scalability,
                performance, and security
                \item Advocated for mob programming practices, improving collaboration, knowledge sharing,
                and code quality
                \item Directed architectural and product decisions to align technical strategies with business
                goals
            \end{itemize}
     
        
        }
        \entry
        {04/2019 -- 10/2021}
        {
            Principal Software Engineer/ Engineering Manager
        }
        {Visma Ltd}
        {\vspace{-10pt}
        \begin{flushleft}
            Led the technical development of Visma's InSchool platform, a cutting-edge educational solution
            serving students and administrators across Norway.
        \end{flushleft}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=15pt]
                
                \item Delivered a high-visibility data integration with the Norwegian government education
                department, onboarding every secondary school student nationwide into the system on
                time for the academic year
                \item Designed scalable backend systems with Java, Spring, and Scala, enhancing platform
                performance and reliability. - Introduced development best practices, resulting in
                measurable improvements in code quality, maintainability, and team efficiency
                \item Mentored teams across multiple roles, fostering a culture of growth through workshops,
                code reviews, and skill-sharing sessions
                \item Acted as the main liaison between development teams and stakeholders, ensuring clear
                communication and timely delivery of priorities
        \end{itemize}

        }
        \entry
        {02/2012 -- 04/2019}
        {
            Senior Software Engineer
        }
        {Topflight Travel Group Ltd}
        {\vspace{-10pt}
        \begin{flushleft}
            Delivered end-to-end development for critical web applications supporting the travel and
            hospitality business at topflight.ie.
        \end{flushleft}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=15pt]
                
                \item Led the design and development of Java-based systems using Spring and Wicket
                frameworks, improving user experience and operational efficiency
                \item Championed the adoption of A3 problem-solving methodologies to identify and address
                technical bottlenecks
                \item Enhanced database performance by optimizing MyBatis with Postgres, ensuring
                seamless data management and retrieval.
                \item Spearheaded Agile adoption and Lean methodologies, improving team efficiency and
                reducing delivery cycles. - Mentored junior developers, fostering a culture of continuous
                learning and professional growth
        \end{itemize}

        }
    
    \end{entrylist}




%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}

\datelessentry{Master of Electronic Systems}{University College Dublin}{Focused on distributed systems and cloud computing.}
\datelessentry{Bachelor of Engineering}{Trinity College Dublin}{ General Engineering Degree with final two years focussed on computer science}


\end{document}
